% Copyright 2004, 2005, 2006 by Ingo Hinrichs, Ulf Klaperski
%
% This file is part of Sigschege - Signal Schedule Generator
% 
% #############################################################################
%
% Sigschege is free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2, or (at your option)
% any later version.
% 
% Sigschege is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
% 
% You should have received a copy of the GNU General Public License
% along with the Sigschege sources; see the file COPYING.  
%
% #############################################################################
%
% $Id$
%
% Sigschege User Manual
%


\documentclass[11pt]{article}

\setlength{\parskip}{1.5ex plus0.5ex minus 0.5ex}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
\Huge Sigschege

\vspace{1cm}

\LARGE User Manual

\vspace{3cm}

Written by Ulf Klaperski

\vspace{1cm}

Created from \verb$Revision$
  
\end{center}

\eject

\section{Introduction}
\label{sec:intro}

Sigschege is an application to create timing diagrams for digital electrical circuits.

Currently the only available user interface is a Python plugin. A graphical user
interface is planned for later releases.

For example scripts please have a look at the examples directory of the
Sigschege source tree.

\section{Anatomy of a Timing Diagram}
\label{sec:anatomy}

\subsection{States and State Maps}
\label{subsec:statemap}

States in Sigschege are defined by a string. The interpretation of this string
is defined by a state map that is usually a property of the signal.  

If a state is not found in the state map it is drawn as ``X'' and the string
will be shown. This way every unkown value will automatically be represented as
a named bus value.

The properties of a state are shown in table \ref{tab:statemap}.

\begin{table}[htbp]
  \centering
  \begin{tabular}[l]{l|l}
    \textbf{Properties}&\textbf{Values}\\\hline
    Visualization&0, 1, X, Z\\
    showString&Boolean\\\hline
  \end{tabular}
  \caption{Properties of a state}
  \label{tab:statemap}
\end{table}

By default every signal has a state map which defines the values 0, 1, Z and
X. These values are defined to be shown without a label with their expected
visualization, which is a bottom line for 0, a top line for 1, a middle line for
Z and top and bottom line for X. If the signal is supposed to represent a bus
which could accidentally have one of the aforementioned values the state map has
to be flushed.


\section{The Python Interface}
\label{sec:python}

\subsection{Running Sigschege}

The \texttt{sigschege} binary is simply an enhanced Python interpreter. The
usual way to create a timing diagram is to write a Python script which uses the
additional functions. We recommend the extension \texttt{.spy} (Sigschege PYthon) for these
scripts. To process a sigschege script just run:

\begin{center}
  \texttt{sigschege my-interface-protocol.spy}
\end{center}


\subsection{Creating a Timing Diagram}

Sigschege implements the \texttt{Sigschege} namespace. To create a timing
diagram just instantiate a \texttt{TimingDiagram} object from this namespace:


\begin{center}
  \texttt{Sigschege.TimingDiagram(<startTime>, <endTime>, <width>, <sliceHeight>)}
\end{center}

This method takes the following arguments:

\begin{table}[htbp]
  \centering
  \begin{tabular}[l]{l|l|l}
    \textbf{Argument}&\textbf{Type}&\textbf{Description}\\\hline
    startTime&float&Start time of the diagram\\
    endTime&float&End time of the diagram\\
    width&float&\texttt{[optional]} Width of the timing diagram\\
    % TODO:default 8.0
    sliceHeight&float&\texttt{[optional]}default height of a single
    slice\\\hline
    % TODO: default 1.0, explain what a slice is
  \end{tabular}
  \caption{Arguments for TimingDiagram}
  \label{tab:timdiagram}
\end{table}

The result of this function must be stored in a variable for later access. A real call will
look like:

\begin{center}
  \texttt{td = Sigschege.TimingDiagram(0.0, 50.0)}
\end{center}

Or maybe:

\begin{center}
  \texttt{td = Sigschege.TimingDiagram(startTime=0.0, endTime=50.0, width=10.0, )}
\end{center}

\subsection{Implementing Signals}
\label{sec:sig}

Signals can be created with \texttt{createSignal}. It can take the following
arguments:

\begin{description}
\item[label] The label which will be printed in the text area on the left side.
\item[isBus] If the signal is a bus. This means all signals are displayed with the X visual
and the state printed. If isBus is 0 the signal is assumed to be a boolean. 
\item[defaultSlope] \emph{optional} The default slope for all events. Default is 0.
\item[before] \emph{optional} Another element of the timing diagram to insert this element before.  
\end{description}

\begin{center}
  \texttt{sig\_clk = td.createSignal(label='Clock', defaultSlope=0.5)}
\end{center}

\subsection{Creating Events}
\label{sec:evt}

Events can be added to an existing signal with the \texttt{addEvent} method.

\texttt{<signal>.addEvent(<time>, <state>)}

The \texttt{state} determines the value of the new state. The visualization of
the state is defined by the state map of the signal. 

In order to draw a '1' state:

\texttt{clock.addEvent(50, '1')}

If the signal uses the \texttt{boolean} state map, the 1 will be displayed as a
top line with no label. The \texttt{bus} state map would display it as top and
bottom line with the 1 as a label.


\subsection{Instantiating a Time Scale}
\label{sec:tis}



\subsection{Exporting Timing Diagrams}
\label{sec:exp}

\subsection{Creating State Maps}
\label{sec:tis}

A new state map can be created with the command:

\begin{center}
  \texttt{<var> = Sigschege.StateMap()}
\end{center}

This freshly created state map is empty and thus has the same effect as the
\texttt{bus} state map. To add state definitions

\begin{center}
  \texttt{<stateMap>.state(<arguments>)}
\end{center}

The arguments accepted by the \texttt{state} method are:

\begin{description}
\item[name] The name of the state.
\item[showState] The state string will we printed as a label.
\item[visual] Defines the visual to be used as a string. Possible values are 1, 0, Z and X.
\end{description}

Example:

\texttt{boolmap = Sigschege.StateMap()}\\
\texttt{boolmap.state(name='1', showState=False, visual='1')}\\
\texttt{boolmap.state(name='0', showState=False, visual='0')}\\
\texttt{boolmap.state(name='Z', showState=False, visual='Z')}\\

This would actually create a map which is identical to the \texttt{boolean}
state map.


\end{document}

